\papertitle

### 2014-03-16 final-report/paper.tex
Added macros

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}

@@

% What the user sees
% Why did we choose the visualization
% How it is implemented

>>>>

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graphview}{Physical Query Plan View\xspace}
\newcommand*{\fragmentview}{Fragment Execution View\xspace}
\newcommand*{\networkview}{Worker Communication View\xspace}
\newcommand*{\overallview}{Fragment Overall View\xspace}

@@

The first step in designing \system was to identify the possible causes that
could affect the execution performance of the query. After we identified
several such causes, that we will enumerate below, we leveraged visualization
techniques that we found fit to allow developers/programmers to get insight
into how the query was executed on the available resources and quickly
identify the source(s) of the performance penalty.

We found that the performance of the query might be affected by the following
factors, which influenced :
\begin{itemize}
   \item 
\end{itemize}

% Why did we choose the visualization
